\section{Existing EUV wave detection algorithms}\label{sec:existing}

Automated feature detection algorithms have an advantage over human
detections of features because they generate repeatable results for
the same input data, i.e. they enable reproducability. In addition,
their ability to examine large quantities of data faster than human
analysis is invaluable in the SDO era, which produces ~1 TB of solar
data each day. The solar physics community already makes use of the
Computer Aided CME Tracking (CACTus: \cite{2004A&A...425.1097R}) and
Solar Eruptive Event Detection System (SEEDS:
\cite{2008SoPh..248..485O}) CME catalogs, both of which are generated
from automated feature detection algorithms.

When relying on such automated procedures, it is scientifically
valuable to have multiple independently designed and developed
automatic feature detection algorithms for the same type of feature as
they allow for cross-checking and verification of results.  By
comparing the final results, the operation of each feature detection
algorithm can be better understood. For example,
\cite{2013ApJ...768..162P} shows that eruption rates from both the
CACTus and SEEDS CME catalogs are systematically higher in 2003-2012
compared to 1997-2002, consistent with the weakness of the late cycle
23 polar fields.  Use of detections from two independently developed
automated CME detection algorithms greatly strengthens this result.

In terms of EUV waves, there are at least two automated EUV wave
detection methods currently published, the Novel EUV wave Machine
Observing algorithm, described by \cite{2005SoPh..228..265P} (see also
\cite{2012SoPh..276..479P}) and the Coronal Pulse Identification and
Tracking Algorithm described in \cite{2014SoPh..289.3279L}. NEMO was
originally designed for analysis of SOHO/EIT data, but has since been
modified to analyze STEREO/EUVI images. The original NEMO algorithm
\cite{2005SoPh..228..265P} consists of three components. These are 1)
source event detection, 2) recognition of eruptive dimmings, 3)
detection and analysis of EUV waves. The event detection component is
based on the higher-order moments of running difference (RD) images. A
RD image is simply the difference between two consecutive images. A
sharp change in the skewness or kurtosis of the distribution of RD
image values is a reliable signature that an impulsive event, such as
a flare or an EUV wave, has been observed in that image. Once a source
detection has occurred, the second and third components of NEMO are
triggered to identify eruptive dimmings and EUV waves respectively.
NEMO assumes that EUV waves propagate circularly from the originating
event. The wave front is found by integrating RD images in nested
annuli centered on the originating event.  Plotting these integrals as
a function of radial distance from the originating event shows a
leading intensity enhancement which is identified as the EUV wave.
Results from NEMO are available at \url{http://sidc.be/nemo/};
however, the implementation ceased operations in 2010 and so there are
no new EUV detections being provided to the community.
\cite{2012SoPh..276..479P} is concerned with advances to original NEMO
algorithm with respect to source event detection and eruptive
dimmings, and does not explicitly tackle EUV waves.

The second algorithm that has been developed is CorPITA
\citep{2014SoPh..289.3279L}. CorPITA uses percentage base-difference
(PBD) images as the foundation for detection (Fig. 2, top row).  A PBD
image is formed by taking the difference between a selected base image
and the current image, and then scaling that difference by the base
image, multiplied by 100.  CorPITA is triggered by the occurrence of a
flare.  In CorPITA PBD images, the base image is taken two minutes
before the flare start time. The flare position is used as the origin
of the EUV wave; great circles intersecting this origin are analyzed
to identify whether an EUV wave is present. The intensity profile
along the great circle is fitted for each time-step with a
multi-Gaussian function, based on the observation of
\cite{2006ApJ...645..757W} that cross-sections of EUV wave events have
this approximate form. This assumption allows the wave to be
characterized in terms of its position, velocity and width. Events and
data products generated by CorPITA are intended to be made available
within the HEK \citep{hek2012, 2012SoPh..275...79M}.  

In this context, AWARE provides a new, alternative approach for the
detection and characterization of EUV waves.  In the following
Sections, we describe in detail the imaging processing steps in AWARE,
and demonstrate its application to solar data.
