\section{Future improvements and data products}\label{sec:future}

Several future refinements are currently planned in order to improve AWARE and maximize its effectiveness and use to the solar community. First among these is integration with the Heliophysics Event Knowledgebase (HEK), which will allow AWARE to operate as a fully automated, triggered algorithm. In future developments, AWARE will monitor the HEK event lists for new events such as solar flares, and the appearance of a new event will trigger subsequent analysis. The HEK record information will be used to determine parameters of the analysis, such as start and end times of the interval to be analysed, and potential locations on the Sun of a wave origin.

Related to this, another development will be the production of a searchable AWARE event catalogue, to be made freely available to the heliophysics community. This is the ultimate goal of AWARE. In this pipeline, each analysis carried out by AWARE will result in a new catalogue record. These records will contain data products of use to the solar community, such as event identifiers, association with any triggering event, quality and size measurements, and dynamical properties of the detected wave, such as velocity and acceleration. This AWARE catalogue will be made available through dissemination tools currently used by the heliophysics community, such as the HEK and the Virtual Solar Observatory (VSO). The availability of such a catalogue will allow large-scale statistical studies of EUV waves and their properties.
