
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                
%%      SWSC LaTeX class for Journal of Space Weather and Space Climate
%%      
%%                                      (c) Springer-Verlag HD
%%                                      revised by EDP Sciences
%%                                      further revised by J. Watermann 
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%      This demonstration file was derived from aa.dem
%%  
%%      AA vers. 7.0, LaTeX class for Astronomy & Astrophysics
%%      demonstration file
%%                                                (c) Springer-Verlag HD
%%                                                revised by EDP Sciences
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%      modified for Journal of Space Weather and Space Climate
%%      by Jurgen Watermann, Editorial Advisor to SWSC
%%
%%      01-04-2012
%%      02-04-2012 revision 1
%%      12-07-2012 revision 2
%%      06-12-2012 revision 3 
%%      01-01-2014 revision 4
%%      06-03-2014 revision 4.1
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%      The two sub-figures referenced in this template are of eps and png type,
%%      respectively, in order to demonstrate the usepackages subfigure and
%%      epstopdf and thus create pdf-only output 
%%
%%      If you want to use TexLive or MikTex together with a bibtex bibliography 
%%      file you may run Latex2e from the command line 
%%          pdflatex -shell-escape swsc.tex
%%          bibtex swsc (do not include an extension such as .tex or .bib)
%%          pdflatex -shell-escape swsc.tex
%%          pdflatex -shell-escape swsc.tex
%%
%%      A double call to pdflatex after calling bibtex is necessary in order to
%%      set citations and references correctly and insure that foreward/backward  
%%      linkage (backref option) is properly applied
%%      If you use MikTex you may need to make a triple call to pdflatex
%%
%%      If you are using TexLive or MikTex but not a bibtex type of bibliography
%%      you may simply run Latex2e twice from the command line 
%%          pdflatex -shell-escape swsc.tex
%%          pdflatex -shell-escape swsc.tex
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   single column 12-point version for review
%%

%%  with traditional abstract
\documentclass[referee,a4paper,12pt,traditabstract]{swsc} 

%%  with structured abstract 
%\documentclass[referee,a4paper,12pt,structabstract]{swsc} 

\usepackage{graphicx}
\usepackage{txfonts}
\usepackage{subfigure}
\usepackage{epstopdf}
\usepackage{lineno}
\usepackage[authoryear,round]{natbib}
\usepackage[backref]{hyperref}
\usepackage{url}

%%    This version assumes using bibtex with the swsc bibliography style file
\bibliographystyle{swsc}

\hypersetup{colorlinks=true,citecolor=cyan,urlcolor=cyan,linkcolor=blue}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{linenumbers}

\title{AWARE: An algorithm for the automated detection and characterization
  of EUV waves in the solar atmosphere}


   \subtitle{ }
   
   \titlerunning{An algorithm for the automated detection of EUV waves}

   \authorrunning{Ireland et al.}


%\input{authors}

\author{J. Ireland\inst{1,}\inst{2}\and
        A. R. Inglis\inst{2,}\inst{3}\and
        A. Y. Shih\inst{2}\and
        S. Christe\inst{2}\and
        S. Mumford\inst{4}\and
        L. A. Hayes\inst{5}\and
        B. J. Thompson\inst{2}
          }

\institute{ADNET Systems, Inc.\\
\email{\href{mailto:jack.ireland@nasa.gov}{jack.ireland@nasa.gov}}
\and
NASA Goddard Space Flight Center, MC 671.1, Greenbelt, MD 20771.
\and
Physics Department, The Catholic University of America,Washington, DC, 20064
\and
Solar Physics and Space Plasma Research Centre (SP$^{2}$RC), School of Mathematics and Statistics, The University of Sheffield, Hicks Building, Hounsfield Road, Sheffield S3 7RH, UK.
\and
School of Physics, Trinity College Dublin, Dublin 2, Ireland.
}


\abstract{Extreme ultraviolet (EUV) waves are large-scale propagating
disturbances observed in the solar corona, frequently associated with
coronal mass ejections and flares. Since their discovery, over two
hundred papers discussing their properties, causes and physical nature have
been published. However, despite this their fundamental properties and the physics of
their interactions with other solar phenomena are still not
understood. To further the understanding of EUV waves, we have constructed the Automated
Wave Analysis and REduction (AWARE) algorithm for the detection of EUV
waves over the full Sun. The AWARE algorithm is based on a novel image
processing approach to isolating the bright wavefront of the EUV as it
propagates across the corona.  AWARE detects the presence of a
wavefront, and measures the distance, velocity and acceleration of
that wavefront across the Sun.  The algorithm is applied to
simulations of EUV wave propagation and to observed data.  Suggestions
are also given for further refinements to the basic algorithm presented
here.}

\keywords{giant planet formation -- $\kappa$-mechanism -- stability of gas spheres}

\maketitle

\input{1-Introduction}

\input{2-Existing}

\input{3-AWARE}

\input{4-Results}

\input(5-Future_work}

\input{5-Conclusions}

\input{acknowledgements}

\bibliography{eitwave-paper.bib}
\bibliographystyle(swsc}

\end{linenumbers}

\end{document}
